\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-07-26 doc/USER_MANUAL/01_introduction.tex
Buildbot ran the code beautifier.
updates doc

\red{SECOND ANNOUNCEMENT: SPECFEM3D can now perform coupling with an external code (DSM, AxiSEM or FK) based on a database of displacement vectors and traction vectors
on the outer edges of the mesh created once and for all (see \cite{MoChKoFu13,MoChKoWa15,WaChMoKoMo16,ToChKoBaLi14,ToKoTsHuChBaLi14}, and if you use that feature of the code please cite at least one of these papers).} \\
To use coupling with FK, just use the set of parameters that is in the DATA/Par\_file input file of the code: \\
\#----------------------------------------------------------- \\
\# \\
\# Coupling with an injection technique (DSM, AxiSEM, or FK) \\
\# \\
\#----------------------------------------------------------- \\
COUPLE\_WITH\_INJECTION\_TECHNIQUE = .false. \\
INJECTION\_TECHNIQUE\_TYPE        = 3   \# 1 = DSM, 2 = AxiSEM, 3 = FK \\
MESH\_A\_CHUNK\_OF\_THE\_EARTH       = .false. \\
TRACTION\_PATH                   = ./DATA/AxiSEM\_tractions/3/ \\
FKMODEL\_FILE                    = FKmodel \\
RECIPROCITY\_AND\_KH\_INTEGRAL     = .false.   \# does not work yet \\
That part (coupling with FK) is actively maintained and works fine. See e.g. \url{http://komatitsch.free.fr/preprints/GRL_Ping_Tong_2014.pdf} for some examples.
There is also an example that is provided with the code: specfem3d/EXAMPLES/small\_example\_coupling\_FK\_specfem. \\
Regarding coupling with DSM, that part is not actively maintained any more, but it is still included in the code, you may have to test it again and make minor adjustments if needed. The necessary tools are in directory specfem3d/EXTERNAL\_PACKAGES\_coupled\_with\_SPECFEM3D/DSM\_for\_SPECFEM3D , and there is a README file in specfem3d/EXTERNAL\_PACKAGES\_coupled\_with\_SPECFEM3D that should be more or less up-to-date (there are about four steps to follow in total, the first one being creating the database of DSM tractions and displacements on the edges of the coupling box). \\
See e.g. \url{http://komatitsch.free.fr/preprints/GJI1_Vadim_2013.pdf} and \url{http://komatitsch.free.fr/preprints/GJI2_Vadim_2015.pdf} for some examples.\\

\red{THIRD ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-).
Note that SPECFEM3D can also model transient gravity perturbations induced by earthquake rupture, as developed and explained in \cite{HaAmBaChMoSoWh2015}.
These are two different things, and both are implemented and avaible in SPECFEM3D.
To use the second feature, please refer to doc/how\_to/README\_gravity\_perturbation.txt.}\\

>>>>

\red{SECOND ANNOUNCEMENT: SPECFEM3D can now perform coupling with an external code (DSM, AxiSEM or FK) based on a database of displacement vectors and traction vectors
on the outer edges of the mesh created once and for all (see \cite{MoChKoFu13,MoChKoWa15,WaChMoKoMo16,ToChKoBaLi14,ToKoTsHuChBaLi14}, and if you use that feature of the code please cite at least one of these papers).} \\
To use coupling with FK, just use the set of parameters that is in the DATA/Par\_file input file of the code: \\
%
\begin{verbatim}
#-----------------------------------------------------------
#
# Coupling with an injection technique (DSM, AxiSEM, or FK)
#
#-----------------------------------------------------------
COUPLE_WITH_INJECTION_TECHNIQUE = .false.
INJECTION_TECHNIQUE_TYPE        = 3       # 1 = DSM, 2 = AxiSEM, 3 = FK
MESH_A_CHUNK_OF_THE_EARTH       = .false.
TRACTION_PATH                   = ./DATA/AxiSEM_tractions/3/
FKMODEL_FILE                    = FKmodel
RECIPROCITY_AND_KH_INTEGRAL     = .false. # does not work yet
\end{verbatim}
That part (coupling with FK) is actively maintained and works fine. See e.g. \url{http://komatitsch.free.fr/preprints/GRL_Ping_Tong_2014.pdf} for some examples.
There is also an example that is provided with the code: specfem3d/EXAMPLES/small\_example\_coupling\_FK\_specfem. \\
Regarding coupling with DSM, that part is not actively maintained any more, but it is still included in the code, you may have to test it again and make minor adjustments if needed. The necessary tools are in directory \texttt{specfem3d/EXTERNAL\_PACKAGES\_coupled\_with\_SPECFEM3D/DSM\_for\_SPECFEM3D}, and there is a \texttt{README} file in \texttt{specfem3d/EXTERNAL\_PACKAGES\_coupled\_with\_SPECFEM3D} that should be more or less up-to-date (there are about four steps to follow in total, the first one being creating the database of DSM tractions and displacements on the edges of the coupling box). \\
See e.g. \url{http://komatitsch.free.fr/preprints/GJI1_Vadim_2013.pdf} and \url{http://komatitsch.free.fr/preprints/GJI2_Vadim_2015.pdf} for some examples.\\

\red{THIRD ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-).
Note that SPECFEM3D can also model transient gravity perturbations induced by earthquake rupture, as developed and explained in \cite{HaAmBaChMoSoWh2015}.
These are two different things, and both are implemented and avaible in SPECFEM3D.
To use the second feature, please refer to \texttt{doc/how\_to/README\_gravity\_perturbation.txt}.}\\
